\documentclass{article} 

\usepackage[a4paper,margin=2cm,left=2cm,right=2cm]{geometry} 
\usepackage[UKenglish]{babel}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}

% Example
% \DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\GL}{GL}

\usepackage{graphicx}
\graphicspath{{./images/}}

% UNCOMMENT IF USING REFERENCES
% \usepackage[notes, backend=biber]{biblatex-chicago}
% \addbibresource{refs.bib} 

\title{Algebra}
\author{joel}
\date{}

\begin{document}

\maketitle

\section*{Common groups and other useful facts} 

\begin{itemize}

    \item $S_n$ is the symmetric group, ways of ordering $n$ elements. $|S_n| =n!$

    \item $D_n$ is the dihedral group, giving the symmetries of an $n$-gon. 
        $|D_n| = 2n$ (identity, n-1 rotations and n reflections)

    \item $\GL(n, \R)$ is the set of invertible $n \times n$ matrices. $\GL(n,
        \Z_p)$ is the set of invertible $n \times n$ matrices with entries in
        $\Z_p$ if $p$ is prime. These sets are groups under matrix
        multiplication. 

    \item It is useful to think of injection as "not losing information" and
        surjection as "hits everything". 

    \item A valid binary operation is one for which you have $a, b \in S$ and 
        $a * b \in S$, or that you can see it as a mapping of $S \times S \to S$.


\end{itemize}

If $S$  and $T$  are finite sets then how many maps are there $S \to T$?
$|S||T|$

\begin{proof} 
    If we consider the mapping $f: S \to T$ then all the possible mapping of a
    given $S$ to some $T$ as $S \times T$. The element $S$ can be mapped to any
    $T$, and so for one $S$ there is $T$ options, with $S$ necessary inputs. As
    such, there is (from Corollary 0.2.2) $|S||T|$ mappings. 
\end{proof} 

Here's all 24 permutations of $S_4$ in cycle notation. The key thing to
remember is that not all of the combinations are made up of one cycle, there
are also the compositions of two cycles (and for $S_n$ when $n>4$ combinations
of 2 and 3, etc.)

\begin{gather*}
    \text{Identity}, \\
    (1 2), (1 3), (1 4), (2 3), (2 4), (3 4), \\
    (1 2 3), (1 2 4), (1 3 4), (2 3 4), \\
    (1 3 2), (1 4 2), (1 4 3), (2 4 3), \\
    (1 2 3 4), (1 2 4 3), (1 3 2 4), (1 3 4 2), (1 4 3 2), (1 4 2 3) \\
    (1 2)(3 4), (1 3)(2 4), (1 4)(2 3)
\end{gather*}

$ \text{some text here} $


\end{document}
